About this Prototype

### 2020-06-17 prototype/explanatory text.Rmd
moved key files to prototype folder; modified app file to include if_then for calc_prior function
navbar structure for UI; explanatory text in seperate tabset

---
title: "Application Outline"
output: 
  github_document:
       pandoc_args: --webtex
bibliography: references.bib
---

@@

## Aim

@@

## Analysis

To estimate bias, this application relies on two kinds of data: (1) user-inputted data on how an attorney has used strikes in the case before them; and (2) if available, pre-compiled historical data on that attorney's use of strikes in past cases.

@@

Here, we represent $d$ as a distribution of how likely each possible value of $d$ is, given the data we have. This lets us depict how confident we should be in inferring bias from the data we have.

The dashed lines indicate a pre-set _credible interval_, i.e., here the values of $d$ between which 80% of the likely values of $d$ fall. If zero falls within this interval, then we should be wary about (have low confidence in) inferring bias (for or against the cognizable class) from the strike data. If zero falls outside this interval, we should feel confident in inferring bias from the strike data. As we get more data, we should feel more (or less) confident about particular values of $d$.

The grey graph is the distribution of $d$ values based _only_ on a pre-set distribution of $d$ to reflect a starting point that bias is unlikely, as adjusted by historical strike data, if available. This represents our *prior beliefs* about an attorney's possible bias in using peremptory challenges, before we know anything about how any attorney uses peremptory strikes in the case before us. The blue (for prosecution) and red (for the defense) distributions in the foreground represent our _updated_ expectations after accounting for the user-inputted strike data (in the table on the left).

# References

>>>>

---
title: "About this Prototype"
output: 
  github_document:
       pandoc_args: --webtex
bibliography: references.bib
---

@@

@@

To estimate such bias, this application relies on two kinds of data: (1) user-inputted data on how an attorney has used strikes in the case before them; and (2) if available, available jury-selection data on that attorney's use of strikes in some past cases during 2013-2017 in the federal district court for the District of Connecticut.

### Analysis

@@

Here, we represent $d$ as a distribution of how likely each possible value of $d$ is, given the data we have. This lets us use the curve's width (the distribution's *standard deviation*) to depict how confident we should be in inferring bias from the data we have: The narrower the curve, the more confident we should be.

The dashed lines indicate a pre-set _credible interval_, i.e., here the values of $d$ between which 80% of the likely values of $d$ fall. If zero falls within this interval, then we should be wary about (have low confidence in) inferring bias (for or against the cognizable class) from the strike data. If zero falls outside this interval, we should feel confident in inferring bias from the strike data.

The grey graph depicts $d$ based _only_ on a pre-set distribution of $d$ to reflect a starting point that bias is unlikely, as adjusted by any historical strike data we have. This represents our *prior beliefs* about an attorney's possible bias in using peremptory challenges, before we know anything about how any attorney uses peremptory strikes in the case before us. The red (for prosecution) and blue (for the defense) distributions in the foreground represent our _updated_ expectations after accounting for the user-inputted strike data (in the table on the left).

### References
